Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-03-30 paper_latex_edit - Copy.tex
txs auto checkin

Like most scenarios adopts a single user massive MIMO system in a single cell, in which the base station equips
\begin{math} N_{t} > 1\end{math} transmitting antennas as well as the UE with a single
receiving antennas. An orthogonal frequency division multiplexing (OFDM) system with \begin{math}\ N_{c}\end{math} sub-carriers for FDD downlink massive MIMO is examined. In the OFDM-MIMO system considered in this work, the subcarriers are assumed to maintain orthogonality. 
we will assume base station sends orthogonal pilots for each subcarrier to the UE 
\begin{math}
	n=1,...,N_{c}
\end{math}: let pilot matrix
\begin{math} \textbf{X}_{p,n}\in C^{N_{t}\times T_{p}}  \end{math} be orthogonal
(\begin{math}
	T_{p} \geq N_{t}
\end{math}).
We will assume on  \begin{math}  {n^{th}} \end{math} sub-carriers the received signal at UE will be equal to : 
\begin{equation}
	\textbf{Y}_{p,n}=\textbf{H}_{n}\textbf{X}_{p,n}+\textbf{Z}_{n} 
\end{equation}
where 
\begin{math}
	\textbf{Y}_{p,n} \in C^{N_{r}\times N_{t}} 
(N_{r}=1)
\end{math} is received pilot at \begin{math}  {n^{th}} \end{math} subcarrier,  
\begin{math}
	\textbf{H}_{n} \in  C^{N_{r}\times N_{t}}
\end{math} is the MIMO channel matrix for subcarrier \begin{math} n \end{math}
and \begin{math} \textbf{Z}_{n} \end{math} is AWGN noise with variance \begin{math}  \sigma^{2} \end{math}.

>>>>

Like most scenarios adopts a single user massive MIMO system in a single cell, in which the base station equips
\begin{math} N_{t} > 1\end{math} transmitting antennas as well as the UE with a single
receiving antennas. An orthogonal frequency division multiplexing (OFDM) system with \begin{math}\ N_{c}\end{math} sub-carriers for FDD downlink massive MIMO is examined. In the OFDM-MIMO system considered in this work, the subcarriers are assumed to maintain orthogonality. 
we will assume base station sends orthogonal pilots for each subcarrier to the UE 
\begin{math}
	n=1,...,N_{c}
\end{math}: let pilot matrix
\begin{math} \textbf{X}_{p,n}\in C^{N_{t}\times T_{p}}  \end{math} be orthogonal
(\begin{math}
	T_{p} \geq N_{t}
\end{math}).
We will assume on  \begin{math}  {n^{th}} \end{math} sub-carriers the received signal at UE will be equal to : 
\begin{equation}
	\textbf{Y}_{p,n}=\textbf{H}_{n}\textbf{X}_{p,n}+\textbf{Z}_{n} 
\end{equation}
where 
\begin{math}
	\textbf{Y}_{p,n} \in C^{N_{r}\times N_{t}} 
(N_{r}=1)
\end{math} is received pilot at \begin{math}  {n^{th}} \end{math} subcarrier,  
\begin{math}
	\textbf{H}_{n} \in  C^{N_{r}\times N_{t}}
\end{math} is the MIMO channel matrix for subcarrier \begin{math} n \end{math}
and \begin{math} \textbf{Z}_{n}\in C^{1\times T_{p}} \end{math} is AWGN noise with variance \begin{math}  \sigma^{2} \end{math}.
